### 2022-09-30 reports/paper/03-results.rmd
New revisions

# Get lower and upper 2.5th %tiles
rr <- rr[,.(estimate = estimate[1],
			lower = {
				x <- value
				x[!is.na(x)] <- quantile(x[!is.na(x)], 0.025) - mean(x[!is.na(x)]) + estimate[1]},
			upper = {
				x <- value
				x[!is.na(x)] <- quantile(x[!is.na(x)], 1 - 0.025) - mean(x[!is.na(x)]) + estimate[1]}
			# wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
			# wald.upper = exp(log(estimate[1]) - qnorm(0.025) * sd(log(value)))
			),
	 variable]

@@

# Get lower and upper 2.5th %tiles
risks <- risks[,.(estimate = estimate[1],
			lower = {
				x <- value
				x[!is.na(x)] <- quantile(x[!is.na(x)], 0.025) - mean(x[!is.na(x)]) + estimate[1]},
			upper = {
				x <- value
				x[!is.na(x)] <- quantile(x[!is.na(x)], 1 - 0.025) - mean(x[!is.na(x)]) + estimate[1]}
			# wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
			# wald.upper = exp(log(estimate[1]) - qnorm(0.025) * sd(log(value)))
			),
	 .(variable.risks = variable)]
```

>>>>

# Get lower and upper 2.5th %tiles
rr <- rr[,.(estimate = estimate[1],
			lower = {
				x <- value
				x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 1 - 0.025)},
			upper = {
				x <- value
				x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 0.025)}
			# wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
			# wald.upper = exp(log(estimate[1]) - qnorm(0.025) * sd(log(value)))
			),
	 variable]

@@

# Get lower and upper 2.5th %tiles
risks <- risks[,.(estimate = estimate[1],
			lower = {
				x <- value
				x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 1 - 0.025)},
			upper = {
				x <- value
				x[!is.na(x)] <- 2 * mean(x[!is.na(x)]) - quantile(x[!is.na(x)], 0.025)}
			# wald.lower = exp(log(estimate[1]) + qnorm(0.025) * sd(log(value))),
			# wald.upper = exp(log(estimate[1]) - qnorm(0.025) * sd(log(value)))
			),
	 .(variable.risks = variable)]
```

### 2022-09-30 reports/paper/paper.Rmd
New revisions

**Authors:** Kevin T. Chen^a,b^, Sally Picciotto^b^, Ellen A. Eisen^b^

@@

**Sources of financial support:** Supported by Training Grant T42OH008429, funded by the National Institute for Occupational Safety and Health (NIOSH) / Centers for Disease Control and Prevention (CDC)

@@

**Methods:** We estimated counterfactual risk of NHL from 1985 to 2004 in the UAW-GM cohort of hourly autoworkers exposed to straight, soluble, and synthetic MWF at 3 Michigan plants under hypothetical interventions. We contrasted counterfactual risk under stochastic interventions on average annual exposure to soluble MWF to that under no intervention on exposure. These stochastic interventions included (1) static interventions on soluble MWF that ignore exposure to other types and (2) dynamic interventions that seek to cap total exposure to any type of MWF by intervening on exposure to soluble MWF only.

>>>>

**Authors:** Kevin T. Chen^a,b^, Ellen A. Eisen^b^, Sally Picciotto^b^

@@

**Sources of financial support:** This work was supported by Training Grant T42OH008429 and Research Project Grant R01OH011092, both funded by the National Institute for Occupational Safety and Health (NIOSH) / Centers for Disease Control and Prevention (CDC).

@@

**Methods:** We estimated counterfactual risk of NHL from 1985 to 2004 in the UAW-GM cohort of hourly autoworkers exposed to straight, soluble, and synthetic MWF at 3 Michigan plants under hypothetical interventions. We contrasted counterfactual risk under stochastic interventions on average annual exposure to soluble MWF to that under no intervention on exposure. These stochastic interventions included (1) static interventions on soluble MWF that ignore exposure to other types and (2) dynamic interventions that seek to cap total exposure to any type of MWF by intervening on exposure to soluble MWF only. Static interventions may be more feasible as real-world policy, but dynamic interventions may result in stronger protections.
